\mytitle

### 2023-05-07 chapters/intro.tex
Contribs draft

\section{Contributions}
The remainder of this dissertation is broken into two chapters.
% TODO
%\cref{c:jitsynth} presents \jitsynth and the techniques that enable
%\jitsynth to synthesize in-kernel JIT compilers.
%\cref{c:depsynth} presents \depsynth and the techniques that enable

>>>>

\section{Contributions}
The remainder of this dissertation is broken into two chapters.
\cref{c:jitsynth} introduces \jitsynth and the techniques that enable
\jitsynth to synthesize in-kernel JIT compilers.
By decomposing the search with minicompilers
and efficiently exploring the space with novel metasketches,
\jitsynth is able to synthesize correct JITs that perform
comparably to their hand-written counterparts.

\cref{c:depsynth} presents \depsynth, a tool for automating
crash consistency in storage systems. In \cfref{c:depsynth},
we introduce a new dependency rule language that describes rules
which specify required write-before relationships for a storage system
at runtime. This abstraction over write-before relationships, along
with a new per-litmus-test search, allows \depsynth to synthesize
correct dependency rules for a production system.
Moreover, these generated rules have nearly the same effect on performance
as dependencies hand-written by experts.

Both of these chapters demonstrate
how program synthesis can aid developers in building
correct and performant systems.
